### 2011-07-19 docs/analysis/analysis.tex
add docstring example for parseparticles

The {\tt parseparticles.py} routine in the {\tt python/} subdirectory
can read in \maestro\ particle files containing particle histories
(usually named {\tt timestamp\_??}).  See the discussion in \S~\ref{arch:sec:particles} for details on initialization.  The driver {\tt
  test\_parseparticles.py} shows shows how to use this module to plot
particle histories.

>>>>

The {\tt parseparticles.py} routine in the {\tt python/} subdirectory
can read in \maestro\ particle files containing particle histories
(usually named {\tt timestamp\_??}).  See the discussion in
\S~\ref{arch:sec:particles} for details on initializing particles in
\maestro.  The driver {\tt test\_parseparticles.py} shows shows how to
use this module to plot particle histories.  Additional documentation
is available from the module itself.  In the python environment,
type:
\begin{lstlisting}[language=Python]
import parseparticles
help(parseparticles)
\end{lstlisting}
to get information on the classes and functions provided by the {\tt
  parseparticles} module.
